---
title: "p8105_hw1_maf2311"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

```{r}
data("penguins", package = "palmerpenguins")
```

Penguins Dataset Description: 

* The Penguins dataset has the following variables: `r names(penguins)`. This data is from the year `r min(pull(penguins, year))` to `r max(pull(penguins, year))`, and includes the following species of penguins: `r unique(pull(penguins, species))`.
* The Penguins dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.
* The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` millimeters.

```{r, echo = FALSE}
plot_penguins =
  tibble(
    bill_length_mm_x = pull(penguins, bill_length_mm),
    flipper_length_mm_y = pull(penguins, flipper_length_mm)
  )
ggplot(plot_penguins, aes(x=bill_length_mm_x, y=flipper_length_mm_y, color = pull(penguins, species))) + geom_point()

ggsave("penguins_scatter_plot.pdf", height = 4, width = 6)
```

# Problem 2

This is my dataframe: 

```{r dataframe, echo = FALSE}
hw1_prob2_df = tibble(
  rand_samp = rnorm(10),
  vec_logical = rand_samp > 0,
  vec_char = c(sample(LETTERS, 10, replace=FALSE)),
  vec_factor = factor(c("a","b","c","a","b","c","a","b","c","a"))
)
hw1_prob2_df
```

I am able to take the mean of the rand_samp variable because it is an integer, and I am able to 
take the mean of the logical variable because it is binary, and are considered 0 = False, and 
1 = True. I cannot take the mean of a character variable or a factor variable.

```{r means, include = FALSE}
mean(pull(hw1_prob2_df, rand_samp))
mean(pull(hw1_prob2_df, vec_logical))
mean(pull(hw1_prob2_df, vec_char))
mean(pull(hw1_prob2_df, vec_factor))
```

```{r convert_types, eval = FALSE}
as.numeric(pull(hw1_prob2_df, vec_logical))
as.numeric(pull(hw1_prob2_df,vec_char))
as.numeric(pull(hw1_prob2_df,vec_factor))
```

When I apply the as.numeric function, the logical, character, and factor variables get assigned an
integer, and then the mean can be calculated. 






