---
title: "p8105_hw1_maf2311"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

```{r}
data("penguins", package = "palmerpenguins")
```

Penguins Dataset Description: 

* The Penguins dataset has the following variables: `r names(penguins)`. This data is from the year `r min(pull(penguins, year))` to `r max(pull(penguins, year))`, and includes the following species of penguins: `r unique(pull(penguins, species))`.
* The Penguins dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.
* The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` millimeters.

```{r, echo = FALSE}
plot_penguins =
  tibble(
    bill_length_mm_x = pull(penguins, bill_length_mm),
    flipper_length_mm_y = pull(penguins, flipper_length_mm)
  )
ggplot(plot_penguins, aes(x=bill_length_mm_x, y=flipper_length_mm_y, color = pull(penguins, species))) + geom_point()

ggsave("penguins_scatter_plot.pdf", height = 4, width = 6)
```

# Problem 2











